Computational musicology, ????, Profit

### 2016-07-25 paper.tex
Clarify a paragraph.

This is a stylistic and a methodological departure from many previous papers on computational musicology. For example, Eduardo
Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda write that ``computational musicology is broadly defined as the
study of Music by means of computer modelling and simulation"\cite{Computational Musicology}. Coutinho et al. approach
computational musicology from a mathematical and a scientific perspective, but this paper will take a mathematical foundation
and build on it with analysis and criticism more common to the literary field.

>>>>

This is a stylistic and a methodological departure from many previous papers on computational musicology. For example, Eduardo
Coutinho, Marcelo Gimenes, Joao M. Martins and Eduardo R. Miranda write that ``computational musicology is broadly defined as the
study of Music by means of computer modelling and simulation"\cite{Computational Musicology}, a description that does not admit
literary analysis. While Coutinho et al. approach computational musicology from a mathematical and a scientific perspective,
I will take a mathematical foundation and build on it with analysis and criticism more common to the literary field.
